---
title: "PPP Unsupervised Categorization"
author: "Evan Doughty"
date: "4/1/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Data is the Macroecological Database of Mammalian Body Mass (MOM_4.1)
### Smith etal 2003

# Large Herbivore Guild

```{r}
mom.data <- read.csv("/Users/emdoughty/Dropbox/Code/R/Carnivore Paleobio Seminar/MOM_v4.1.csv")
#mom.data <- read.csv("/Users/emdoughty/Dropbox/Code/R/Carnivore Paleobio Seminar/MOM_v4.1_herb.csv")


mom.data <- mom.data[,c("Continent", "Species.Distribution", "Status", 
                        "Order", "FAMILY", "Genus", "Species", 
                        "Combined.Mass..g.","LogMass..g.", "Combined.Mass..kg.", "LogMass..kg."),]

mom.data <- mom.data[mom.data$Order %in% c("Artiodactyla", "Perissodactyla"),]

### set groups using Janis 2000 breaks
bmBreaks_herb <- c(-Inf, 0.69897, 1.39794, 2.176091, 2.69897, Inf) #Janis 2000  max(measure.mat$bodyMass, na.rm=TRUE)
sizecateg <- c("<5 kg", 
               "5-25 kg",
               "25-150kg", 
               "150-500 kg", 
               ">500 kg")
mom.data$Janis.cat <- NA
require(cluster)

for(ii in seq(1, length(sizecateg),1)) 
{
  mom.data[mom.data$LogMass..kg. > bmBreaks_herb[ii] & mom.data$LogMass..kg. < bmBreaks_herb[ii+1],]$Janis.cat <- sizecateg[ii]
}

colors.Janis <- rainbow(length(sizecateg)); names(colors.Janis) <- sizecateg
```

## k-means

```{r}
kmeans_results <- list()
kmeans_breaks <- list()

wss <- vector(length = 9)
sil <- vector(length = 9)

for(ii in seq(2,10,1))
{
  kmeans_results[[ii]] <- kmeans(mom.data$LogMass..kg., centers = ii, iter.max = 10000, nstart = 50)
  wss[ii-1] <- kmeans_results[[ii]]$tot.withinss
  sil[ii-1] <- mean(silhouette(kmeans_results[[ii]]$cluster, dist(mom.data$LogMass..kg.))[,3])
  
  kmean_Onebreaks <- matrix(ncol = 3, nrow = ii)
  colnames(kmean_Onebreaks) <- c("k", "min.kg", "max.kg")
  
  for(jj in seq(1, max(unique(kmeans_results[[ii]]$cluster)),1)) 
  {
    min.categ <- min(mom.data[kmeans_results[[ii]]$cluster == jj,"LogMass..kg."])
    max.categ <- max(mom.data[kmeans_results[[ii]]$cluster == jj,"LogMass..kg."])
    
    kmean_Onebreaks[jj,] <- c(jj, min.categ, max.categ)
  }
  kmeans_breaks[[ii]] <- kmean_Onebreaks[order(kmean_Onebreaks[,2],kmean_Onebreaks[,3]),]
}
```

```{r}
#good resource and code to follow
##https://uc-r.github.io/kmeans_clustering

if(interval.type == "bins")
{
  png(paste0("/Users/emdoughty/Dropbox/Proposal/Chapter 1 Figures/Kmeans herbivores Unsup Curve and Silhoette 2 Ma Intervals 64 to 0 Ma ", date.save,".png"),
      width = 6, height = 4, units = "in", res = 200)
}

if(interval.type == "nalma")
{
  png(paste0("/Users/emdoughty/Dropbox/Proposal/Chapter 1 Figures/Species Richness Plots for Pred Diet Draft NALMA ", date.save,".png"),
      width = 15, height = 9, units = "in", res = 200)
}

#Determine Optimal K value
par(mfrow=c(1,2), bg=NA)
##Elbow Method
plot(2:10, wss, type = "b", pch = 19,
     xlab = "", ylab = "", xaxt= 'n', yaxt = 'n')
    # xlab = "Number of clusters K", ylab = "Total Within Sum of Square")
abline(v=5)
axis(1,col.ticks="white", col.axis = "white", cex.axis =1, labels = TRUE, at = c(seq(2,10,by = 2)), lwd = 2, tck = -0.05, las = 1, padj = 0.75)
axis(2,col.ticks="white", col.axis = "white", cex.axis =1, labels = TRUE, at = c(seq(0,25,by = 5)), lwd = 2, tck = -0.05, las = 1,  hadj = 1.5)

##Silhoettes
plot(2:10, sil, type = "b", pch = 19,
     #xlab = "Number of clusters K", ylab = "Average Silhoettes")
     xlab = "", ylab = "", xaxt= 'n', yaxt = 'n')
abline(v=5)
axis(1,col.ticks="white", col.axis = "white", cex.axis =1, labels = TRUE, at = c(seq(2,10,by = 2)), lwd = 2, tck = -0.05, las = 1, padj = 0.75)
axis(2,col.ticks="white", col.axis = "white", cex.axis =1, labels = TRUE, at = c(seq(0.40,0.6,by = 0.01)), lwd = 2, tck = -0.05, las = 1,  hadj = 1.5)

dev.off()
```

```{r}
#Plot PPP pred Categories vs Optimal K Means
if(interval.type == "bins")
{
  png(paste0("/Users/emdoughty/Dropbox/Proposal/Chapter 1 Figures/Kmeans herbivores 5_6 Unsup size cat 2 Ma Intervals 64 to 0 Ma ", date.save,".png"),
      width = 6, height = 4, units = "in", res = 200)
}

if(interval.type == "nalma")
{
  png(paste0("/Users/emdoughty/Dropbox/Proposal/Chapter 1 Figures/Species Richness Plots for Pred Diet Draft NALMA ", date.save,".png"),
      width = 15, height = 9, units = "in", res = 200)
}

par(mfrow=c(1,3), bg=NA)
plot(mom.data$LogMass..kg., pch = 19, col = colors.Janis[mom.data$Janis.cat], #main = "Janis 2000",
     xlab = "", ylab = "", xaxt= 'n', yaxt = 'n', col.lab = "white")
abline(h = bmBreaks_herb)
text(75, bmBreaks_herb, labels = bmBreaks_herb, pos = 3, adj = 1)
#axis(1,col.ticks="white", col.axis = "white", cex.axis =1, labels = FALSE, at = c(seq(2,10,by = 2)), lwd = 2, tck = -0.05, las = 1, padj = 0.75)
axis(2,col.ticks="white", col.axis = "white", cex.axis =1, labels = TRUE, at = c(seq(0,4,by = 0.5)), lwd = 2, tck = -0.05, las = 1,  hadj = 1.5)

k<-5
plot(mom.data$LogMass..kg., pch = 19, col = rainbow(k)[kmeans_results[[k]]$cluster], #main = paste0("K = ",k),
     xlab = "", ylab = "", xaxt= 'n', yaxt = 'n', col.lab = "white")
#abline(h= kmeans_results[[5]]$centers)
#abline(h=jenkBreaks[2:(length(jenkBreaks)-1)])
#text(jenkBreaks[2:(length(jenkBreaks)-1)], labels =jenkBreaks[2:(length(jenkBreaks)-1)], pos = 3)
for(yy in seq(2, nrow(kmeans_breaks[[k]]),1)) 
  {
    abline(h=c((kmeans_breaks[[k]][yy-1,3]+kmeans_breaks[[k]][yy,2])/2))
    text( x = 50, y = (kmeans_breaks[[k]][yy-1,3]+kmeans_breaks[[k]][yy,2])/2, 
         labels = (kmeans_breaks[[k]][yy-1,3]+kmeans_breaks[[k]][yy,2])/2,
         pos = 3, adj = 1)
}
axis(2,col.ticks="white", col.axis = "white", cex.axis =1, labels = FALSE, at = c(seq(0,4,by = 0.5)), lwd = 2, tck = -0.05, las = 1,  hadj = 1.5)

k<-6
plot(mom.data$LogMass..kg., pch = 19, col = rainbow(k)[kmeans_results[[k]]$cluster],# main = paste0("K = ",k),
     xlab = "", ylab = "", xaxt= 'n', yaxt = 'n', col.lab = "white")
#abline(h= kmeans_results[[5]]$centers)
for(yy in seq(2, nrow(kmeans_breaks[[k]]),1)) 
  {
    abline(h=c((kmeans_breaks[[k]][yy-1,3]+kmeans_breaks[[k]][yy,2])/2))
    text( x = 50, y = (kmeans_breaks[[k]][yy-1,3]+kmeans_breaks[[k]][yy,2])/2, 
         labels = (kmeans_breaks[[k]][yy-1,3]+kmeans_breaks[[k]][yy,2])/2,
         pos = 3, adj = 1)
}
axis(2,col.ticks="white", col.axis = "white", cex.axis =1, labels = FALSE, at = c(seq(0,4,by = 0.5)), lwd = 2, tck = -0.05, las = 1,  hadj = 1.5)
dev.off()
```
#### Note for plots above.  Horizontal lines for K-means plots are the average between the min and max of the upper and lower intervals, respectively.   Jenks breaks are the same so those would be more reliable.


## Natural Breaks (Jenks Optimization)

```{r}
require(BAMMtools)

vec <- mom.data$LogMass..kg.
#get the withinss to find optimal breaks and compare with kmeans
cal_wss <- function(values, group){
                    if(is.numeric(group)){
                      group = factor(group)
                    }
                    sum((aov(values~group)$residuals^2))
                  }

j_withinss = sapply(2:10, function(i){
                    Jenk = getJenksBreaks(vec, i+1)
                    clus = cut(vec, breaks=Jenk, include.lowest=TRUE)
                    cal_wss(vec,clus)
                  })

par(mfrow = c(1,2))
plot(2:10, wss, type = "b", pch = 19,
     xlab = "Number of clusters K", ylab = "Total Within Sum of Square", main = "k-means")
abline(v=5)
plot(2:10, j_withinss, xlab = "k", ylab = "Total Within Sum of Square", main = "Jenk")
abline(v=5)
```

#### Plot the optimal Jenk
```{r}
require(GmAMisc)
```

```{r}
par(mfrow = c(1,2))
plotJenks(mom.data$LogMass..kg., n = 5, brks.cex = 1, dist = 4, top.margin = 20)
plotJenks(mom.data$LogMass..kg., n = 6, brks.cex = 1, dist = 4, top.margin = 20)
```

##############################################################################################################################

# Predator Guild

```{r}
#removed taxa that were under scrutiny and those with a weight of -999
mom.data <- read.csv("/Users/emdoughty/Dropbox/Code/R/Carnivore Paleobio Seminar/MOM_v4.1_pred.csv")
mom.data <- mom.data[!mom.data$FAMILY %in% c("Otariidae","Odobenidae","Phocidae"),]

mom.data <- mom.data[,colnames(mom.data) %in% c("Status", 
                        "Order", "FAMILY", "Genus", "Species", 
                        "Combined.Mass..g.","LogMass..g.", "Combined.Mass..kg.", "LogMass..kg.")]

mom.data <- mom.data[mom.data$Order %in% c("Carnivora"),]

### set groups using PPP prey breaks
bmBreaks_pred <- c(-Inf, 0, 0.845098, 1.322219, 2, Inf)  #Janis 2000  max(measure.mat$bodyMass, na.rm=TRUE)
sizecateg <- c("<1kg",
               "1-7kg",
               "7-21kg", 
               "21-100kg",
               ">100kg")
mom.data$Pred.cat <- NA

for(ii in seq(1, length(sizecateg),1)) 
{
  mom.data[mom.data$LogMass..kg. > bmBreaks_pred[ii] & mom.data$LogMass..kg. < bmBreaks_pred[ii+1],]$Pred.cat <- sizecateg[ii]
}

colors.pred <- rainbow(length(sizecateg)); names(colors.pred) <- sizecateg

kmeans_results <- list()
kmeans_breaks <- list()

wss <- vector(length = 9)
sil <- vector(length = 9)

for(ii in seq(2,10,1))
{
  kmeans_results[[ii]] <- kmeans(mom.data$LogMass..kg., centers = ii, iter.max = 10000, nstart = 50)
  wss[ii-1] <- kmeans_results[[ii]]$tot.withinss
  sil[ii-1] <- mean(silhouette(kmeans_results[[ii]]$cluster, dist(mom.data$LogMass..kg.))[,3])
  
  kmean_Onebreaks <- matrix(ncol = 3, nrow = ii)
  colnames(kmean_Onebreaks) <- c("k", "min.kg", "max.kg")
  
  for(jj in seq(1, max(unique(kmeans_results[[ii]]$cluster)),1)) 
  {
    min.categ <- min(mom.data[kmeans_results[[ii]]$cluster == jj,"LogMass..kg."])
    max.categ <- max(mom.data[kmeans_results[[ii]]$cluster == jj,"LogMass..kg."])
    
    kmean_Onebreaks[jj,] <- c(jj, min.categ, max.categ)
  }
  kmeans_breaks[[ii]] <- kmean_Onebreaks[order(kmean_Onebreaks[,2],kmean_Onebreaks[,3]),]
}
```

```{r}
#good resource and code to follow
##https://uc-r.github.io/kmeans_clustering

if(interval.type == "bins")
{
  png(paste0("/Users/emdoughty/Dropbox/Proposal/Chapter 1 Figures/Kmeans predators Unsup Curve and Silhoette 2 Ma Intervals 64 to 0 Ma ", date.save,".png"),
      width = 6, height = 4, units = "in", res = 200)
}

if(interval.type == "nalma")
{
  png(paste0("/Users/emdoughty/Dropbox/Proposal/Chapter 1 Figures/Species Richness Plots for Pred Diet Draft NALMA ", date.save,".png"),
      width = 15, height = 9, units = "in", res = 200)
}

#Determine Optimal K value
par(mfrow=c(1,2), bg=NA)
##Elbow Method
plot(2:10, wss, type = "b", pch = 19,
     xlab = "", ylab = "", xaxt= 'n', yaxt = 'n')# xlab = "Number of clusters K", ylab = "Total Within Sum of Square")
abline(v=6)
axis(1,col.ticks="white", col.axis = "white", cex.axis =1, labels = TRUE, at = c(seq(2,10,by = 2)), lwd = 2, tck = -0.05, las = 1, padj = 0.75)
axis(2,col.ticks="white", col.axis = "white", cex.axis =1, labels = TRUE, at = c(seq(0,80,by = 10)), lwd = 2, tck = -0.05, las = 1,  hadj = 1.5)

##Silhoettes
plot(2:10, sil, type = "b", pch = 19,
     xlab = "", ylab = "", xaxt= 'n', yaxt = 'n') # xlab = "Number of clusters K", ylab = "Average Silhoettes")
abline(v=6)
axis(1,col.ticks="white", col.axis = "white", cex.axis =1, labels = TRUE, at = c(seq(2,10,by = 2)), lwd = 2, tck = -0.05, las = 1, padj = 0.75)
axis(2,col.ticks="white", col.axis = "white", cex.axis =1, labels = TRUE, at = c(seq(0,0.585,by = 0.005)), lwd = 2, tck = -0.05, las = 1,  hadj = 1.5)

dev.off()
```

```{r}
if(interval.type == "bins")
{
  png(paste0("/Users/emdoughty/Dropbox/Proposal/Chapter 1 Figures/Kmeans predators 2_5_6 Unsup size cat 2 Ma Intervals 64 to 0 Ma ", date.save,".png"),
      width = 8, height = 4, units = "in", res = 200)
}

if(interval.type == "nalma")
{
  png(paste0("/Users/emdoughty/Dropbox/Proposal/Chapter 1 Figures/Species Richness Plots for Pred Diet Draft NALMA ", date.save,".png"),
      width = 15, height = 9, units = "in", res = 200)
}

#Plot PPP pred Categories vs Optimal K Means
par(mfrow=c(1,4), bg=NA)
plot(mom.data$LogMass..kg., pch = 19, col = colors.pred[mom.data$Pred.cat], #main = "PPP Categories")
       xlab = "", ylab = "", xaxt= 'n', yaxt = 'n', col.lab = "white")
abline(h = bmBreaks_pred)
text(75, bmBreaks_pred, labels = bmBreaks_pred, pos = 3, adj = 1)
axis(2,col.ticks="white", col.axis = "white", cex.axis =1, labels = TRUE, at = c(seq(-2,4,by = 1)), lwd = 2, tck = -0.05, las = 1,  hadj = 1.5)

k<-2
plot(mom.data$LogMass..kg., pch = 19, col = rainbow(k)[kmeans_results[[k]]$cluster],# main = paste0("K_",k))
       xlab = "", ylab = "", xaxt= 'n', yaxt = 'n', col.lab = "white")
#abline(h= kmeans_results[[5]]$centers)
for(yy in seq(2, nrow(kmeans_breaks[[k]]),1)) 
  {
    abline(h=c((kmeans_breaks[[k]][yy-1,3]+kmeans_breaks[[k]][yy,2])/2))
    text( x = 50, y = (kmeans_breaks[[k]][yy-1,3]+kmeans_breaks[[k]][yy,2])/2, 
         labels = (kmeans_breaks[[k]][yy-1,3]+kmeans_breaks[[k]][yy,2])/2,
         pos = 3, adj = 1)
}
axis(2,col.ticks="white", col.axis = "white", cex.axis =1, labels = FALSE, at = c(seq(-2,4,by = 1)), lwd = 2, tck = -0.05, las = 1,  hadj = 1.5)

k<-5
plot(mom.data$LogMass..kg., pch = 19, col = rainbow(k)[kmeans_results[[k]]$cluster], #main = paste0("K_",k))
       xlab = "", ylab = "", xaxt= 'n', yaxt = 'n', col.lab = "white")
#abline(h= kmeans_results[[5]]$centers)
for(yy in seq(2, nrow(kmeans_breaks[[k]]),1)) 
  {
    abline(h=c((kmeans_breaks[[k]][yy-1,3]+kmeans_breaks[[k]][yy,2])/2))
    text( x = 50, y = (kmeans_breaks[[k]][yy-1,3]+kmeans_breaks[[k]][yy,2])/2, 
         labels = (kmeans_breaks[[k]][yy-1,3]+kmeans_breaks[[k]][yy,2])/2,
         pos = 3, adj = 1)
}
axis(2,col.ticks="white", col.axis = "white", cex.axis =1, labels = FALSE, at = c(seq(-2,4,by = 1)), lwd = 2, tck = -0.05, las = 1,  hadj = 1.5)

k<-6
plot(mom.data$LogMass..kg., pch = 19, col = rainbow(k)[kmeans_results[[k]]$cluster],# main = paste0("K_",k))
       xlab = "", ylab = "", xaxt= 'n', yaxt = 'n', col.lab = "white")
#abline(h= kmeans_results[[5]]$centers)
for(yy in seq(2, nrow(kmeans_breaks[[k]]),1)) 
  {
    abline(h=c((kmeans_breaks[[k]][yy-1,3]+kmeans_breaks[[k]][yy,2])/2))
    text( x = 50, y = (kmeans_breaks[[k]][yy-1,3]+kmeans_breaks[[k]][yy,2])/2, 
         labels = (kmeans_breaks[[k]][yy-1,3]+kmeans_breaks[[k]][yy,2])/2,
         pos = 3, adj = 1)

}
axis(2,col.ticks="white", col.axis = "white", cex.axis =1, labels = FALSE, at = c(seq(-2,4,by = 1)), lwd = 2, tck = -0.05, las = 1,  hadj = 1.5)
dev.off()
```

#### Note for plots above.  Horizontal lines for K-means plots are the average between the min and max of the upper and lower intervals, respectively.  Jenks breaks are the same so those would be more reliable.


## Natural Breaks (Jenks Optimization)

```{r}
require(BAMMtools)

vec <- mom.data$LogMass..kg.
#get the withinss to find optimal breaks and compare with kmeans
cal_wss <- function(values, group){
                    if(is.numeric(group)){
                      group = factor(group)
                    }
                    sum((aov(values~group)$residuals^2))
                  }

j_withinss = sapply(2:10, function(i){
                    Jenk = getJenksBreaks(vec, i+1)
                    clus = cut(vec, breaks=Jenk, include.lowest=TRUE)
                    cal_wss(vec,clus)
                  })

par(mfrow = c(1,2))
plot(2:10, wss, type = "b", pch = 19,
     xlab = "Number of clusters K", ylab = "Total Within Sum of Square", main = "k-means")
abline(v=5)
plot(2:10, j_withinss, xlab = "k", ylab = "Total Within Sum of Square", main = "Jenk")
abline(v=5)
```

#### Plot the optimal Jenk
```{r}
par(mfrow = c(1,3))
plotJenks(mom.data$LogMass..kg., n = 2, brks.cex = 1, dist = 4, top.margin = 25)
plotJenks(mom.data$LogMass..kg., n = 5, brks.cex = 1, dist = 4, top.margin = 25)
plotJenks(mom.data$LogMass..kg., n = 6, brks.cex = 1, dist = 4, top.margin = 25)
```


# Predator with Diet

```{r}
#Gower distance?



```

# Time series
```{r}
#Dynamic time warping = compare seperate time series

#Moving average
###may be problematic with NALMA dataset due to unequal time intervals
```
